Swintons tend to be people that create tools for themselves and share them with others once they are finished or at least usable, thereby conforming to \href{http://www.catb.org/jargon/html/H/hacker-ethic.html}{hacker ethic} in the first sense of it. From the creativity and hands-on mentality on the different servers, more than a few projects and hundreds of lines of code resulted.

\section{pre-installed}
All the servers came with a variety of programs already installed and at the hands of users. These included IRC client (e.g. irssi), mail clients like mutt or alpine, several text editors (vim, emacs, nano to name a few).

$\sim$jstg of ctrl-c.club \href{http://ctrl-c.club/~jstg/available_programs.html}{listed packages installed on said server}, which seres as an example.

\section{Games}
While a collection of games was already installed on several (if not all) tilde servers, many users created their own. Those are of all kinds. $\sim$cortex lists a text maze, a text adventure, a platformer and more on \href{http://www.tilde.club/~cortex/games.html}{the tilde.arcade}.\\

On squiggle.city, \href{https://squiggle.city/~zinefer/}{$\sim$zinefer} created another arcade.

\section{Webrings}
\href{https://en.wikipedia.org/wiki/Webring}{Webrings} are remnants of the WWW from the nineties. Since tilde servers aim to bring back the fun of past times, it did not last long until this technique was re-invented.
\\

$\sim$harper on tilde.club began work on \href{http://tilde.club/~harper/join.html}{a webring} in October 2014 and \href{https://github.com/harperreed/harper.tilde/}{shared the code} like a good swinton. A user count seems not available.
\\

The \href{http://tilde.town/~um/tilde_ring/join.html}{tilde.town $\sim$ring} was initiated in December 2014 and has \href{http://tilde.town/~um/tilde_ring/members.html}{71 members} as of 2016-09-08. The source code building this ring was shared \href{https://github.com/jamesandariese/tilde.town.webring}{on GitHub}, too.
\\

germantil.de appeared to have a webring, but it is \href{http://web.archive.org/web/20141025180728/http://germantil.de/~ahava/webring.html}{gone for good}.
\\

On tilde.club, \href{http://tilde.club/~notjosh/}{$\sim$notjosh} took this whole thing to extremes by writing an actual 3D webring in HTML and JavaScript.

\section{Blogs}
Multiple users on different tilde servers also noticed that CLI blogging tools were either not installed or just did not fit them right, so they took matters into their own hands approached the problem in different ways.
\\
\begin{itemize}
	\item $\sim$minerobber wrote a \href{https://github.com/MineRobber9000/blog-gen}{blog generator} in Python for his tilde.town site
	\item on totallynuclear.club, $\sim$schlink created \href{https://github.com/sts10/radiation}{Radiation} using Ruby
	\item ctrl-c.club's $\sim$philips wrote \href{https://github.com/felipetavares/bake/blob/master/README.md}{bake} in C, later re-implemented it in C++
	\item tilde.center had $\sim$papa scripting Stream Of Consciousness in sh, which was slightly edited by $\sim$pgadey on ctrl-c.club (Official source code not available.)
  \item tilde.town offers \href{http://tilde.town/~endorphant/ttbp/}{ttbp}, coded by $\sim$endorphant
	\item on ctrl-c.club, again, $\sim$gauntlet wrote \href{https://github.com/gauntletm/gmb}{gmb}, using bash
\end{itemize}

\section{Polls}
$\sim$philips \href{http://ctrl-c.club/~philips/index.html#Poll}{wrote about} a bash script that allows to create polls on tilde servers. Directory-based and to be used on the CLI. Simple. Source code \href{https://github.com/felipetavares/poll}{on GitHub}, of course.

\section{Activity}
Multiple users have found one way or another to display the activity on the servers.
\begin{itemize}
	\item \href{http://tilde.town/~sharp/size.html}{size of public\_html per user} on tilde.town
	\item \href{http://tilde.town/~ags/updated.html}{pages updated in the last 24 hours} on tilde.town
	\item \href{http://www.ctrl-c.club/~pgadey/updated.html}{recently updated pages} on ctrl-c.club
	\item \href{http://ctrl-c.club/~greymtr/logs/}{chat logs} on ctrl-c.club
	\item \href{http://ctrl-c.club/~gauntlet/o/online.html}{average of logged in users} on ctrl-c.club
	\item \href{http://tilde.club/~delfuego/tilde.24h.html}{pages updated in last 24 hours} on tilde.club
\end{itemize}

Another example was \href{http://tilde.club/~globz/alice.txt}{Alice}. She gained health points whenever users edited their web pages, but lost 12 points per hour. After activity on tilde.club began to cease, Alice eventually died.

\section{Overview}
There are lists of public readable projects on \href{http://ctrl-c.club/~bear/code.html}{ctrl-c.club} and \href{http://tilde.town/~audy/code.html}{tilde.town}.
